Data-driven approaches to identifying knowledge gaps in marine invertebrate biodiversity

### 2017-05-31 manuscript.Rmd
simplify code/dependencies for sampling + diversity maps

These results suggest that even when considering species lists that have been curated and that represent possibly the most accurate knowledge for this geographic area, today we could only reconstruct these lists partially based on digitized information. For instance, based on OBIS data the list would be at `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Porifera"]*100)`% complete for sponges to `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs. However, these levels drop significantly if we consider species for which museum specimens are available from  `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs to `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Annelida"]*100)`% for annelids.
It highlights that additional digitization is necessary but even more importantly additional collecting is needed to validate the occurences of the species included in these lists.

@@

@@

![Number of species of marine invertebrates](figures/map_diversity.pdf)

![Number of museum records for marine invertebrates](figures/map_sampling_effort.pdf)

![Number of species of marine invertebrates](figures/map_diversity.pdf)

>>>>

These results suggest that even when considering species lists that have been curated and that represent possibly the most accurate knowledge for this geographic area, today we could only reconstruct these lists partially based on digitized information. For instance, based on OBIS data the list would be `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Porifera"]*100)`% complete for sponges to `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs. However, these levels drop significantly if we consider species for which museum specimens are available from  `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs to `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Annelida"]*100)`% for annelids. Similar patterns can be observed for the Pacific Northwest, but overall the levels of data availability are lower: from `r format_output(summary_richness_per_db_koz$prop_obis_in_pnw[summary_richness_per_db_koz$taxon_name == "Porifera"]*100)`% for sponges to `r format_output(summary_richness_per_db_koz$prop_obis_in_pnw[summary_richness_per_db_koz$taxon_name == "Annelida"]*100)`% for annelids for the proportion of species that have records in OBIS, and from  `r format_output(summary_richness_per_db_koz$prop_idigbio_in_pnw[summary_richness_per_db_koz$taxon_name == "Porifera"]*100)`% for sponges to `r format_output(summary_richness_per_db_koz$prop_idigbio_in_pnw[summary_richness_per_db_koz$taxon_name == "Mollusca"]*100)`% for molluscs for the proportion of species that have records in iDigBio. Museum specimens are critical to validate the occurence of species [@Rocha2014], especially for marine invertebrates for which species limits based on morphology have been known to be challenged by other lines of evidence including molecular data [@Knowlton2000]. Some of the discrepencies observed between the number of species for which occurence data and museum specimens are available suggest that additional digitization of collections (including capturing their geographic information) are needed.

@@

```{r map-diversity-sampling, fig.cap='Spatial distribution of the number of samples (A) and species richness (B) for marine invertebrates based on specimen data available from iDigBio within the limits of the Exclusive Economic Zone for the contiental USA.'}
knitr::include_graphics("figures/map_diversity_sampling.pdf")
```

@@
